Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-08-22 paper/v3.0/sections/5_floquet_drude_conductivity.tex
Re-structure

% ****** Start of file dressed_quantum_hall.tex ****** %

\documentclass[
 reprint,
 amsmath,amssymb,
 aps,
 prb,
]{revtex4-2}

%===============================================================================
% Import packages
%===============================================================================
% Bold math
\usepackage{bm}
% AMS packages
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
% Physics package
\usepackage{physics}
% SI units package
\usepackage{siunitx}
% Hypertext package
\usepackage[breaklinks=true,colorlinks=true,linkcolor=blue,urlcolor=blue,citecolor=blue]{hyperref}
% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
%===============================================================================
% Bibliography style
\bibliographystyle{apsrev4-2}

\begin{document}

\preprint{APS/123-QED}

%===============================================================================
% Title of the manuscript
%===============================================================================
\title{A generalized model for the charge transport properties of dressed quantum Hall systems}
%===============================================================================

%===============================================================================
% Authors of the manuscript
%===============================================================================
\author{Kosala Herath,}
\email{kosala.herath@monash.edu}
\author{Malin Premaratne}
\email{malin.premaratne@monash.edu}
\affiliation{Advanced Computing and Simulation Laboratory (A$\chi$L), Department of Electrical and Computer Systems Engineering, Monash University, Clayton, Victoria 3800, Australia.}
%===============================================================================

%===============================================================================
% Add date
%===============================================================================
\date{\today}
%===============================================================================

%===============================================================================
% Abstract
%===============================================================================
\begin{abstract}
We present a generalized mathematical model for predicting the transport properties of a quantum system exposed to a stationary magnetic field and a high-intensity electromagnetic field.
The new formulation, which applies to two-dimensional(2D) dressed quantum Hall systems, is based on Landau quantization theory and Floquet-Drude conductivity approach.
We model our system as a two-dimensional electron gas (2DEG) that interacts with two external fields. To analyze the strong light coupling with the 2DEG, we employ the Floquet theory as a nonperturbative procedure.
Moreover, the Floquet-Fermi golden rule is adopted to explore the impurity scattering effects on charge transport in disordered quantum Hall systems.
We derive fully analytical expressions to describe longitudinal components in the conductivity tensor in dressed quantum Hall systems.
Subsequently, we demonstrate that the conductivity characteristics of quantum Hall systems can be manipulated using strong external light.
Our results align with well-established and experimentally
verified theoretical descriptions for undressed systems while providing a more generalized analysis of the conductivity characteristics in quantum Hall systems.
Thus, our model can be applied to accurately interpret the usage of strong external radiation as a tool in nanoscale quantum devices.
\end{abstract}
%===============================================================================

%===============================================================================
% Make title of the manuscript
%===============================================================================
\maketitle
%===============================================================================

%===============================================================================
% Section 01 : Introduction
%===============================================================================
\section{\label{sec:introduction} Introduction}

Manipulating light-matter interactions in the quantum regime paved the path for an astonishing number of useful technologies in the last century. Quantum optics, which study these interactions, have drawn research attention to the disciplines of optoelectronics \cite{liu16,wijesekara20,tao21,wijesekara21}, sensing \cite{rodrigo15,pirandola18,hapuarachchi2018}, energy harvesting \cite{weeraddana15,yuan16,sun18},
quantum computing \cite{huh15,slussarenko19,andersen21}, bio-information \cite{marais18,bian20}, and many other specialities of recent technologies \cite{rivera20}.
The studies on quantum optics of nanostructures were generally centered on metamaterials \cite{shalaev07,si14}, quantum plasmonic effects \cite{hapuarachchi19,perera20}, lasers and amplifiers \cite{chow13,jayasekara16,premaratne17}, and quantum cavity physics \cite{tsang10,liu17,devi20}.
However, in recent years, one of the foremost aims of examining nanostructures under external radiation was understanding their electron transport characteristics \cite{kitagawa11,zhou11,kibis14,pervishko15,morina15,dehghani15,dini16,wackerl20}.

Better understanding the fundamental mechanisms of charge transport can allow us to invent novel nanoelectronic devices and optimize their performance \cite{premaratne21}.
Most recent studies on the subject have considered the driving field as a perturbation field \cite{pervishko15,morina15}. However, this assumption breaks down for systems under high-intensity illuminations \cite{grifoni98,wackerl20}.
Modeling an electromagnetic field under a perturbative formalism involves expanding the interaction terms in powers of the field intensity. At high intensities, the higher-order terms influence the physics more strongly and the basis of the perturbative treatment begins to break down.
In these instances, a more accurate treatment needs to be adopted. Thus, we treat the interacting fermion system and the radiation as one combined quantum system, namely dressed system \cite{morina15,cohen98,scully01}. Here the applied high-intensity  electromagnetic field identify as the \textit{dressing field}.

Theoretical analyses on the transport properties of dressed fermion systems were recently reported in Refs. \cite{kibis14,morina15,wackerl20}.
Furthermore, in Ref. \cite{wackerl20} a general expression for conductivity in a dressed system has been derived in a fully closed analytical form. In their study, a novel type of Green’s functions, namely four-times Green’s functions were used to derive the Floquet-Drude conductivity formula. This opened the path for exploring and exploiting nanostructures' charge transport attributes under an intense dressing field.

Quantum Hall effect \cite{girvin90} observed in two-dimensional (2D) fermion systems at low temperatures under strong stationary magnetic fields manifest remarkable magneto-transport behaviors. Transport properties of these systems have recently attracted both theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{allerman95,tieke97,pan05} interest.
Endo \textit{et al.} \cite{endo09} presented the calculations of longitudinal and transverse conductivity tensor components and their relationship in a quantum Hall system. These theoretical calculations  align better with experimental observations compared to previous studies.

In contrast, we can observe more exciting phenomena by simultaneously applying a dressing field to a quantum Hall system already under a non-oscillating magnetic field.
Whilst there exist several leading theories for calculating conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, these studies  have not been utilized to describe the optical manipulation of charge transport.
Recently, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall systems. However, they have not adopted the state-of-the-art model to describe the conductivity in a quantum Hall system. In their study, they used the conductivity models from Refs. \cite{ando74_1,ando82}, and as mentioned in Endo \textit{et al.} \cite{endo09}, those models predict a semi-elliptical broadening against Fermi level for each Landau level and provide less agreement with the empirical results.

In the present analysis, we introduce a robust mathematical model for a dressed two-dimensional electron gas (2DEG) subject to another nonoscillating magnetic field.
A stationary magnetic field is applied perpendicularly across the surface of the 2DEG system. This causes the orbital motion of the electrons to be quantized, and a discrete energy spectrum with Landau splitting is observed \cite{landau30}.
In this study, we explicitly calculate the longitudinal components ($\sigma^{xx},\sigma^{yy}$) of the conductivity tensor in a periodically driven quantum Hall system by developing a generalized analytical description using the Floquet-Drude conductivity \cite{wackerl20}.
Finally, we demonstrate that our generalized model reproduces the results of the state-of-the-art conductivity model in Ref. \cite{endo09}, which was developed for the more specific case of quantum Hall systems without the external dressing field.
Moreover, we find that the optical field can be used as a mechanism to regulate transport behavior in numerous 2D nanostructures which can serve as a basis for many useful nanoelectronic devices. We believe that our theoretical analysis and visual depictions of numerical results will lead to a better understanding of manipulating charge transport. Moreover, this will inspire advanced  developments in nanoscale quantum devices.

The paper is organized as follows. Sec.  \ref{sec:schrodinger_problem} introduces our dressed quantum Hall system and the exact wave function solutions for the given configuration. Sec. \ref{sec:floquet_theory} provides the Floquet theory interpretation of these wave functions.
We introduce Floquet-Fermi golden rule for a quantum Hall system in Sec. \ref{sec:inverse_scattering_time}, and use it in Sec. \ref{sec:floquet_drude_conductivity} to derive analytical expressions for longitudinal components of conductivity.
The derived theoretical model is further analyzed numerically using empirical system parameters and compared with previous studies in Sec. \ref{sec:manipulate_conductivity}.
In Sec. \ref{sec:conclusions}, we summarize our analysis and present our conclusions.
%===============================================================================

%===============================================================================
% Section 02 : Schrodinger problem for a dressed quantum Hall system
%===============================================================================
\section{\label{sec:schrodinger_problem} Schrodinger Problem for a Dressed Quantum Hall System}

Our system consists of a 2DEG placed on the $xy$-plane of the three-dimensional coordinate space. In our analysis, the 2DEG is subjected to a nonoscillating magnetic field $\vb{B} = (0,0,B)^{T}$, which is pointed towards the $z$-axis. In addition, a linearly polarized strong light is applied perpendicular to the 2DEG surface. We specially select the frequency of the dressing field $\omega$ to be in the off-resonant regime such that the field behaves as a purely dressing field. Furthermore, without limiting the generality, we choose a $y$-polarized electric field $\vb{E} = (0,E\sin(\omega t),0)^{T}$ for the linearly polarized dressing field as given in Fig.~\ref{fig:1}.
\begin{figure}[b]
\includegraphics[scale=0.9]{fig_1_system_diagram}
\caption{\label{fig:1} Our 2DEG system only confined in the $xy$-plane while both of the stationary magnetic field $\vb{B}$ and the dressing field are applied perpendicular to the plane of 2DEG. The dressing field is linearly polarized with a $y$-polarized electric field $\vb{E}$.}
\end{figure}
Here $B$ and $E$ represent the amplitudes of the stationary magnetic field and oscillating electric field, respectively.

Using Landau gauge for the stationary magnetic field, we can represent it as a vector potential $\vb{A}_{s} = (-By,0,0)^{T}$. Furthermore, we model the dynamic dressing field in the Coulomb gauge as $\vb{A}_{d}(t) = (0,[E\cos(\omega t)]/\omega,0)^{T}$. These vector potentials are coupled to the momentum of 2DEG as kinetic momentum \cite{mahan00,bruus04}. Thus, we can represent our system with a time-dependent Hamiltonian
\begin{equation} \label{eq:1}
  \hat{H}_e(t) =
  \frac{1}{2m_e}
  \left\{ \hat{\vb{p}} - e\right[ \vb{A}_{s}+\vb{A}_{d}(t) \left] \right\}^2,
\end{equation}
where $m_e$ is the effective electron mass, $e$ is the magnitude of the electron charge, and $\hat{\vb{p}} = (\hat{p}_x,\hat{p}_y,0)^{T}$ represents the canonical momentum operator for 2DEG with electron momentum $(p_{x},p_{y},0)^{T}$.
The exact solutions for the time-dependent Schrödinger equation $i\hbar \dv*{\psi}{t} = \hat{H}_e(t)\psi$ were already derived in Refs. \cite{husimi53,ditt98,dini16}. Here we present them as a set of wave functions defined by two quantum numbers $(n,m)$
\begin{equation} \label{eq:2}
  \begin{aligned}
    &\psi_{n,m}(x,y,t)  \\
      & \quad = \frac{1}{\sqrt{L_x}}
        \chi_n \bm{\left(} y - y_0 - \zeta(t) \bm{\right)}\\
      & \qquad \times
        \exp \bm{\left(}
        \frac{i}{\hbar}\left\{- \epsilon_n t
        + p_x x + \frac{eE}{\omega}(y - y_0)\cos(\omega t) \right.\right.\\
      & \left.\left. \qquad\qquad +
        m_e\dot{\zeta}(t)\left[y - y_0 -\zeta(t)\right] +
        \int_0^{t}L(\zeta,\dot{\zeta},t')\,dt' \right\}\bm{\right)},
  \end{aligned}
\end{equation}
where $n \in \mathbb{Z}^+_0$ and $m \in \mathbb{Z}$. Here $L_{x}$ and $L_{y}$ are dimensions of the 2DEG surface, and $\hbar$ is the reduced Planck constant. The center of the cyclotron orbit on the $y$-axis is given by $y_0 = \flatfrac{-p_x}{(eB)}$ with $p_x = \flatfrac{2\pi\hbar m}{L_x}$.
Moreover, $\chi_n$ are well-known eigenstate solutions for the Schrödinger equation of the stationary quantum harmonic oscillator
\begin{equation} \label{eq:3}
  \chi_n(y) =
  \left( \frac{\kappa}{2^{n}n! \sqrt{\pi}}\right)^{1/2}
  e^{-\kappa^2 y^2/2}
  \mathcal{H}_n \qty(\kappa y),
\end{equation}
with eigenvalues $\epsilon_n = \hbar \omega_0 [n + (1/2)]$ where $\kappa = \sqrt{{m_e \omega_0}/{\hbar}}$, $\mathcal{H}_n(\cdot)$ is the $n$-th Hermite polynomial, and the cyclotron frequency $\omega_0 = eB/m_e$.
We represent the path shift of the driven classical oscillator $\zeta(t)$ by
\begin{equation} \label{eq:4}
  \zeta(t) = \frac{eE}{m_e(\omega_0^2 - \omega^2)}\sin(\omega t),
\end{equation}
and we introduce $\dot{\zeta}(t) = \pdv*{\zeta(t)}{t}$ for the sake of notational ease. We can identify the Lagrangian of the driven classical oscillator $L(\zeta,\dot{\zeta},t)$ as
\begin{equation} \label{eq:5}
  L(\zeta,\dot{\zeta},t) = \frac{1}{2} m_e\dot{\zeta}^2(t) - \frac{1}{2}m_e\omega_0^2 \zeta^2(t) + eE\zeta(t) \sin(\omega t).
\end{equation}
For details of the full derivation, refer to Appendix \ref{appendix_a}.
The exponential phase shifts in Eq.~(\ref{eq:2}) represent the influence of the stationary magnetic field and dressing field on the electron behavior of our system. Therefore, we can renormalize the magneto-transport characteristics of 2DEG by a nonoscillating magnetic field along with a dressing field.
%===============================================================================

%===============================================================================
% Section 03 : Floquet theory perspective
%===============================================================================
\section{\label{sec:floquet_theory} Floquet Theory Perspective}

Symmetry conditions often give useful insights into the behaviors of physical quantum systems.
For instance, the famous Bloch analysis of electrons in quantum systems introduces a mathematical explanation for quantum systems occupying a discrete translational symmetry in the configuration space. Similarly, Floquet theory gives a mathematical formalism that can be used for translational symmetry in time rather than in space \cite{floquet83,grifoni98,holthaus15}.
The Floquet-Drude conductivity theory was employed recently by Wackerl \textit{et al.} \cite{wackerl20} as a method to analyze the transport properties of quantum systems exposed to strong radiation.
In their work, they have presented more accurate results than the former theoretical descriptions for the conductivity of nanoscale systems in the  presence of a dressing field. Therefore, we apply the Floquet-Drude conductivity theory to analyze our 2DEG system which is subjected to both a stationary magnetic field and a dressing field.

First, we need to identify the \textit{quasienergies} and time periodic \textit{Floquet modes} \cite{grifoni98} for the wave functions given in Eq.~(\ref{eq:2}). By factorizing the wave function into a linearly time-dependent part and a periodic time-dependent part, we present the quasienergies with
\begin{equation} \label{eq:6}
  \varepsilon_{n} =
  \hbar \omega_0 \left(n + \flatfrac{1}{2}\right) - \Delta_{\varepsilon},
\end{equation}
which only depends on a single quantum number $n$. Furthermore, we can recognize the Floquet modes as
\begin{equation} \label{eq:7}
  \begin{aligned}
    \phi_{n,m}(x,y,t) =&
    \frac{1}{\sqrt{L_x}} \chi_{n}\bm{\left(}y - y_0 -\zeta(t)\bm{\right)} \\
    & \times
      \exp \bm{\left(}
      \frac{i}{\hbar}\left\{
      p_x x + \frac{eE}{\omega}(y - y_0)\cos(\omega t) \right.\right. \\
    & \left.\left. \qquad\qquad +
      m_e\dot{\zeta}(t)\left[y - y_0 -\zeta(t)\right] +
      \xi \right\}\bm{\right)},
  \end{aligned}
\end{equation}
with
\begin{equation} \label{eq:8}
  \Delta_{\varepsilon} = \frac{e^2E^2}{4m_e(\omega_0^2 - \omega^2)},
\end{equation}
and
\begin{equation} \label{eq:9}
  \xi = \frac{e^2E^2 \left(3\omega^2 - \omega_0^2 \right)}
  {8m_e\omega(\omega_0^2 - \omega^2)^2} \sin(2\omega t).
\end{equation}
For a detailed derivation, refer to Appendix \ref{appendix_b}.
It is important to note that these Floquet modes are time-periodic ($T=2\pi/\omega$) functions. At resonance $\omega = \omega_0$, the energy levels occupy a continuous spectrum and the quasienergy formalism is no longer valid \cite{popov70}. Therefore, in this work we choose a dressing field frequency obeying the condition $\omega \neq \omega_0$.

Performing the Fourier transform over the confined 2D space, we obtain the momentum space ($k_x,k_y$) representation of Floquet modes
\begin{equation} \label{eq:10}
  \begin{aligned}
    \phi_{n,m}\big(k_x,k_y,t\big)  =&
    \sqrt{L_x}
    \widetilde{\chi}_{n} \bm{\left(}k_y - b\cos(\omega t)\bm{\right) }\\
    & \times
    \exp \bm{\left(} i\xi -ik_y  \left[d\sin(\omega t) + y_0 \right] \bm{\right)},
  \end{aligned}
\end{equation}
where
\begin{equation} \label{eq:11}
  \widetilde{\chi}_{n}(k) =
  i^n \left(\frac{1}{ 2^{n} n! \sqrt{\pi} \kappa}\right)^{1/2}
  e^{-\flatfrac{k^2}{(2 \kappa^2)}}
  \mathcal{H}_{n} \left(\flatfrac{k}{\kappa}\right).
\end{equation}
Here we have introduced new parameters
\begin{equation} \label{eq:12}
  b =
  \frac{eE\omega_0^2}{\hbar\omega(\omega_0^2 - \omega^2)},
\end{equation}
and
\begin{equation} \label{eq:13}
  d =
 \frac{eE}{m_e(\omega_0^2 - \omega^2)}.
\end{equation}
Using Floquet theory, we can re-write the wave functions derived in Eq.~(\ref{eq:2}) as the \textit{Floquet states} in momentum space
\begin{equation} \label{eq:14}
  \psi_{n,m}(k_x,k_y,t) =
  \exp(-\flatfrac{i\varepsilon_{n}t}{\hbar}) \phi_{n,m} (k_x,k_y,t).
\end{equation}
%===============================================================================

%===============================================================================
% Section 04 : Inverse scattering time analysis
%===============================================================================
\section{\label{sec:inverse_scattering_time}  Inverse Scattering Time Analysis}

The Floquet-Fermi golden rule was proposed in Ref. \cite{wackerl20} as an approach to analyze the transport properties of dressed quantum systems with impurities.
However, this theory has not been applied for a dressed quantum Hall system in the previous studies. In this analysis, we use Floquet-Fermi golden rule to identify the effects induced by impurities on the magneto-transport properties.
With the help of $t-t'$ formalism \cite{wackerl20,grifoni98,sambe75,peskin93,althorpe97} and applying Floquet states derived in Eq.~(\ref{eq:14}), we can derive an  expression for $(l,l')$-th element of the inverse scattering time matrix for the $N$-th Landau level as
\begin{widetext}
\begin{equation} \label{eq:15}
  \begin{aligned}
    \left(\frac{1}{\tau(\varepsilon,k_x)}\right)^{ll'}_N = &
    \frac{ \pi \hbar\varrho^2}{e^2B^2} \delta(\varepsilon - \varepsilon_N) \\
    & \times
    \int_{-\infty}^{\infty}
    J_l \bm{\left(} \frac{b\hbar}{eB}({k}_x - k_1) \bm{\right)}
    J_{l'} \bm{\left(} \frac{b\hbar}{eB}({k}_x - k_1) \bm{\right)}
    \left|
    \int_{-\infty}^{\infty}
    \chi_N \left( \frac{\hbar}{eB}k_2 \right)
    \chi_N \bm{\left(} \frac{\hbar}{eB}
    \left( k_1 - {k}_x - k_2 \right) \bm{\right)}
    dk_2 \right|^2 d k_1,
  \end{aligned}
\end{equation}
\end{widetext}
where $\varrho = \eta_{imp} L_x \left[\flatfrac{ V_{imp}}{\pi}\right]^{1/2}$, $\varepsilon$ is a given energy value, $J_l(\cdot)$ are Bessel functions of the first kind with $l$-th integer order, and $\varepsilon_N$ is the energy of the $N$-th Landau level.
A more detailed derivation is given in Appendix \ref{appendix_c}.
We modeled the effect caused by impurities in the considered system as a single perturbation potential.
Since random impurities in a disordered metal offer a better approximation for experimental conditions, we assumed that our perturbation potential is formed by a group of randomly distributed impurities.
Thus, we represented the total scattering potential in the 2DEG as a sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$. Here $\eta_{imp}$ is the number of impurities in a unit area, $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}_{imp}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$, and $\braket{x}{k_x} = e^{-ik_x x}$.
Moreover, in this analysis, $\expval{\cdot}_{imp}$ represents the average over the impurity disorder.

Next, we analyze the contribution of the inverse scattering time matrix elements on the transport properties of our system.
Since the disorder in the system can not significantly alter the eigenenergy values of the undressed system \cite{wackerl20}, we can neglect the contribution of all off-diagonal elements in the inverse scattering time matrix. Subsequently, we consider only the central diagonal element (${l=l'=0}$) of the inverse scattering time matrix which has the largest contribution to the transport characteristics. Along with this assumption, we introduce a new parameter as the scattering-induced broadening of the $N$-th Landau level \cite{dini16,endo09}
\begin{equation} \label{eq:16}
 \Gamma^{00}_{N}(\varepsilon,k_x) =
 \hbar \left(\frac{1}{\tau(\varepsilon,k_x)}\right)^{00}_N.
\end{equation}
We can evaluate this as
\begin{widetext}
  \begin{equation} \label{eq:17}
   \begin{aligned}
     &\Gamma^{00}_{N} (\varepsilon,k_x) =
     \frac{ \pi \hbar^2 \varrho^2}{e^2B^2}
     \delta(\varepsilon - \varepsilon_{N})
     \int_{-\infty}^{\infty}
     J_0^2 \bm{\left(} \frac{b\hbar}{eB}({k}_x - k_1) \bm{\right)}
     \left|
     \int_{-\infty}^{\infty}
     \chi_N \left( \frac{\hbar}{eB}k_2 \right)
     \chi_N \bm{\left(} \frac{\hbar}{eB}
     \left( k_1 - {k}_x - k_2 \right) \bm{\right)}
     dk_2 \right|^2 d k_1.
   \end{aligned}
  \end{equation}
In addition, for a scattering scenario taking place within the same Landau level, we are able to present the delta distribution of the energy by the  interpretation \cite{dini16}
\begin{equation} \label{eq:18}
 \delta(\varepsilon - \varepsilon_{N}) \approx
 \frac{1}{\pi \Gamma^{00}_N (\varepsilon,k_x)}.
\end{equation}
Subsequently, we write the central element of inverse scattering time matrix in the more compact form
\begin{equation} \label{eq:19}
  \begin{aligned}
    &\Gamma^{00}_{N}(\varepsilon,k_x) =
     \varrho
      \left[
      \int_{-\infty}^{\infty}
      J_0^2 \bm{\left(} \lambda_1 (k_x - k_1) \bm{\right)}
      \left|
      \int_{-\infty}^{\infty}
      \widetilde{\chi}_{N}\left(\lambda_2 k_2 \right)
      \widetilde{\chi}_{N} \bm{\left(} \lambda_2 (k_1 - k_2 - k_x) \bm{\right)}
      dk_2 \right|^2
      dk_1
      \right]^{-\frac{1}{2}},
  \end{aligned}
\end{equation}
where $ \lambda_1 = \flatfrac{\hbar b}{(eB)}$ and  $\lambda_2 = \flatfrac{\hbar \kappa}{(eB)}$.
To analyze the effects of the dressing field on the scattering-induced broadening, we introduce the normalized $N$-th Landau level scattering-induced broadening as
\begin{equation} \label{eq:20}
    \Lambda_N(k_x) =
    \frac{\Gamma^{00}_N (\varepsilon,k_x)}
    {\Gamma^{00}_{N=0}(\varepsilon,k_x)\big|_{E=0}},
\end{equation}
which we can evaluate with
\begin{equation} \label{eq:21}
    \Lambda_N (k_x) =
    \left[
    \frac
    {
      \int_{-\infty}^{\infty}
      J_0^2 \bm{\left(} \lambda_1 (k_x - k_1) \bm{\right)}
      \left|
      \int_{-\infty}^{\infty}
      \widetilde{\chi}_{N}\left(\lambda_2 k_2 \right)
      \widetilde{\chi}_{N} \bm{\left(} \lambda_2 (k_1 - k_2 - k_x) \bm{\right)}
      dk_2 \right|^2
      dk_1
    }
    {
      \int_{-\infty}^{\infty}
      \left|
      \int_{-\infty}^{\infty}
      \widetilde{\chi}_0 \left(\lambda_2 k_2 \right)
      \widetilde{\chi}_0 \bm{\left(} \lambda_2 (k_1 - k_2 - k_x) \bm{\right)}
      dk_2 \right|^2
      dk_1
    }
    \right]^{1/2}.
\end{equation}
\end{widetext}

\begin{figure}[t]
\includegraphics[scale=0.55]{fig_2_normalized_broadening_with_momentum}
\caption{\label{fig_3} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against $x$-directional momentum value $k_x$ in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a  frequency of $\omega =\SI{2e12}{\radian\per\second}$ and intensity $I =\SI{100}{\watt\per\square\centi\metre}$.
In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
\end{figure}

\begin{figure}[t]
\includegraphics[scale=0.54]{fig_3_normalized_broadening_with_intensity}
\caption{\label{fig_4} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against dressing field intensity $I$, in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a frequency of $\omega =\SI{2e12}{\radian\per\second}$. In this calculation, we have assumed that the natural broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
\end{figure}

Next, we calculated the normalized energy band broadening against $x$-directional momentum component ${k_x}$ for different Landau levels ($N = 0,1,2,3,4$) for GaAs-based quantum well and the results are depicted in Fig.~\ref{fig_3} and Fig.~\ref{fig_4}. To make a comparison, we have selected the experiment parameters to match with analysis in Ref.~\cite{endo09}.
In that study, the authors have assumed that the effective mass of the electron in GaAs-based quantum well system is $m_e \approx 0.07\widetilde{m}_e$ where $\widetilde{m}_e$ is the mass of the electron \cite{endo09,winkler03,wackerl20}. In addition, they used the broadening of the undressed $0$-th Landau level $\Gamma_0$ as $\SI{0.24}{\milli\eV}$. Therefore, in our calculations, we assumed that the natural least Landau level broadening also has this value: $\Gamma^{00}_{N=0}|_{E=0} = \SI{0.24}{\milli\eV}$.
Here, we observe that the normalized energy broadening value for each Landau level is independent of the $x$-directional momentum $k_x$ value and we are able to manipulate it by the dressing field. When the dressing field's intensity increases, the energy broadening is reduced, which leads to changes in the transport properties of the dressed quantum Hall system.
To analyze these adjustments in detail, we derive an analytical expression for the conductivity of a dressed quantum Hall system in the next section.
%===============================================================================

%===============================================================================
% Section 05 : Floquet-Drude Conductivity in a Dressed Quantum Hall System
%===============================================================================
\section{\label{sec:floquet_drude_conductivity} Floquet-Drude Conductivity in a Dressed Quantum Hall System}

@@

%===============================================================================

%===============================================================================
% Section 06 : Manipulate Conductivity in Quantum Hall Systems
%===============================================================================
\section{\label{sec:manipulate_conductivity} Manipulate Conductivity in Quantum Hall Systems}

To identify the longitudinal conductivity characteristics of quantum Hall system under external dressing field, first we derive an expression for normalized longitudinal conductivity as a function of Fermi energy $X_F$ and intensity of the dressing field $I$.
We can identify the normalized $x$-directional longitudinal conductivity of dressed quantum Hall system by
\begin{equation}\label{eq:37}
  \widetilde{\sigma}^{xx}(X_F,I) =
  \flatfrac{\sigma^{xx}}{\sigma_{0}},
\end{equation}
with $\sigma^0 = \flatfrac{e^2}{(\pi \hbar A)}$, and we can express this as
\begin{equation} \label{eq:38}
  \begin{aligned}
    \widetilde{\sigma}^{xx}(X_F,I) &=
    \sum_{n}
    \frac{(n+1)}{\varsigma^2 \Lambda_n \Lambda_{n+1}} \\
    &\quad\times
    \left[
      \frac{1}
      {
        1 + \left(\frac{X_F - n -1}{\varsigma \Lambda_n}\right)^2
      }
    \right]
    \left[
      \frac{1}
      {
        1 + \left(\frac{X_F - n}{\varsigma \Lambda_{n+1}}\right)^2
      }
    \right],
  \end{aligned}
\end{equation}
where $\varsigma = \flatfrac{\Gamma_0}{(2\hbar \omega_0)}$. Here, $\Gamma_0$ is the natural energy broadening of the least Landau level.

As illustrated in Fig.~\ref{fig:5} and Fig.~\ref{fig:6}, we can manipulate the normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ with the applied dressing field's intensity and the Fermi level $X_F$ of the considered system.
For a given dressing field intensity, the longitudinal conductivity varies with  the Fermi level of the system showing sharp peaks at each Landau energy level.
In quantum Hall systems, electrons are restricted to bear only the Landau energies. Thus, the conductivity reduces significantly when the Fermi level is not aligned with any of the Landau levels. In contrast, near each Landau level, the conductivity achieves excessive values compared to other areas. Moreover, as illustrates in Fig.~\ref{fig:5}, the peak value of the normalized longitudinal conductivity on each Landau level gets increased with the Landau level number.

On the other hand, considering the effects of the applied dressing field on the longitudinal conductivity of 2DEG, we can identify that the dressing field has sharpened the conductivity peaks.
When we increase the intensity level of the dressing field, the conductivity regions get weakened as illustrated in the Fig.~\ref{fig:6}.
However, the peak value of the conductivity at each Landau level has the same value as the undressed system. This demonstrates our ability to tune the width of the conductivity regions in these quantum Hall systems with the help of a dressing field.

These characteristics align well with the outcomes demonstrated by Dini \textit{et al.} \cite{dini16}.  As the authors remarked in that publication, since the Fermi level of the system can be changed with the applied gate voltage of the material, this can be utilized as a 2D switch for nanoscale optoelectronics applications. Controlling  the external dressing field's intensity allows us to fine-tune this switching mechanism for optimized performance.
However, we can distinguish that the shapes and behavior of the conductivity regions that illustrated in Fig.~\ref{fig:5} and Fig.~\ref{fig:6} are generally incompatible with the results reported in Ref.~\cite{dini16}. This is due to the selection of the conventional longitudinal conductivity theory of 2DEG from Refs.~\cite{ando74_1,ando82}. The semi-elliptical conductivity regions are  illustrated in Refs.~\cite{dini16,ando74_1,ando82}, have less consistency with the experimentally observed data for Landau levels \cite{endo09}.
In our study of the transport properties of quantum Hall systems, we developed the conductivity expression starting from the Floquet-Drude conductivity \cite{wackerl20} and we achieved outcomes that align with the results depicted in Ref. \cite{endo09}.
The theory on the conductivity of quantum Hall systems in Ref.~\cite{endo09} provides an excellent agreement with the experimentally observed results in GaAs/AlGaAs 2DEG for the low magnetic field range.
However, they have not considered the tunability that can be achieved with a dressing field. In this analysis, we account for both the magnetic and dressing field effects that can affect the transport properties of 2DEG, leading to a more generalized theory. Thus in this study, we were able to demonstrate that using Floquet-Drude conductivity method, one can derive a more generalized mathematical model which fits better with experiment for the charge transport properties of quantum Hall systems.

\begin{figure}[t]
\includegraphics[scale=0.54]{fig_4_conductivity_with_fermi_level}
\caption{ Normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a  frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$. In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
\label{fig:5}
\end{figure}

\begin{figure}[t]
\includegraphics[scale=0.54]{fig_5_conductivity_with_fermi_level_zoomed}
\caption{$3$rd Landau level’s normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$.
In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
\label{fig:6}
\end{figure}
%===============================================================================

%===============================================================================
% Section 07 : Conclusions
%===============================================================================
\section{\label{sec:conclusions} Conclusions}

In this paper, we introduced a generalized mathematical model for predicting  charge transport properties in a 2DEG under a nonoscillating magnetic field and a high-intensity light. Under the uniform magnetic field, the charged particles can only settle in discrete energy values, which leads to the Landau quantization. We modeled the behavior of electrons in Landau levels under the dressing field utilizing the Floquet-Drude conductivity method. We assumed the impurities in the material as a Gaussian random scattering potential. Finally, we derived expressions for x-directional and y-directional longitudinal components of electric conductivity tensor for the considered system.

Our derived analytical expressions disclosed that we are able to control the transport characteristics of the dressed quantum Hall system by the applied dressing field’s intensity. Using detailed numerical calculations with empirical system parameters, we further analyzed the manipulation of conductivity components using the dressing field.
We found that the graphical illustrations that we obtained from these numerical calculations are capable of producing the same behavior as experiments on quantum Hall systems in the absence of a dressing field.
Furthermore, we identified that by increasing the intensity of the radiation, we can squeeze the conductivity regions near the Landau levels. Despite this behavior being identified in previous works, their results did not coincide with the more accurate description of conductivity components in undressed quantum Hall systems. However, our generalized analysis on the conductivity of dressed quantum Hall systems provide a well-suited description for these specific quantum Hall systems.

>>>>

% Section 05 - Floquet-Drude Conductivity in Quantum Hall Systems

@@
